---
title: "R Practice: Functions"
format: html
---
## Load the necessary libraries
```{r}
library(rvest)
library(readr)
library(dplyr)
library(janitor)
library(here)
```

## Load the species table
```{r}
webpage <- rvest::read_html("https://www.pwrc.usgs.gov/BBL/Bander_Portal/login/speclist.php")

tbls <- rvest::html_nodes(webpage, "table") %>% 
    rvest::html_table(fill = TRUE)

species <- tbls[[1]] %>% 
    janitor::clean_names() %>% 
    select(alpha_code, common_name) %>% 
    mutate(alpha_code = tolower(alpha_code))

head(species, 3)
```

## Read in each data file and store the data frame as nest_data, predator_survey, and egg_measures accordingly. After reading the data, insert a new chunk or in the console, explore the data using any function we have used during the lessons (eg. colname(), glimpse())
```{r}
## Reading data
nest_data <-  read_csv(here("data/Utqiagvik_nest_data.csv"))

predator_survey <- read_csv(here("data/Utqiagvik_predator_surveys.csv"))

egg_measures <- read_csv(here("data/Utqiagvik_egg_measurements.csv"))
```

## Explore the data
```{r}
colnames(predator_survey)
glimpse(predator_survey)
unique(predator_survey$species)
summary(predator_survey)
```
## Translate species codes into common names
```{r}
predator_comm_names <- left_join(predator_survey,
                                 species,
                                 by = c("species" = "alpha_code"))
```

## Functions to add species common name to any data frame
```{r}
#' Functions to add species common name to any data frame
#'
#' @param df containing species codes in "species"
#' @param species species codes with "alpha_code" and "common_name"
#'
#' @returns Original data frame with addition of common name of species
#' @export
#'
#' @examples 
#' #' predator_with_names <- assign_species_name(predator_survey, species)
#' head(predator_with_names)
#' 
#' 
assign_species_name <- function(df, species){
    return_df <- left_join(df, species, by = c("species" = "alpha_code"))
    return(return_df)
}
```

## Use the function to clean names of each data frame
```{r}
predator_clean <- assign_species_name(predator_survey, species) %>% 
    select(year, site, date, common_name, count) %>% 
    filter(!is.na(common_name))

nest_location_clean <- assign_species_name(nest_data, species) %>% 
    select(year, site, nestID, common_name, lat_corrected, long_corrected) %>% 
    filter(!is.na(common_name))

eggs_clean <- assign_species_name(egg_measures, species) %>% 
    select(year, site, nestID, common_name, length, width) %>% 
    filter(!is.na(common_name))
```

